---
title: "PageRank Models"
author: "Student id: 22078426"
output: html_document
---

```{r setup}
library(dplyr)
MS<- read.csv("TOP_MS.csv")
WS<- read.csv("TOP_WS.csv")
MD<- read.csv("TOP_MD.csv")
WD<- read.csv("TOP_WD.csv")
XD<- read.csv("TOP_XD.csv")
latesttour<- read.csv("tourID.csv",header = FALSE) 
latesttourID<- latesttour$V1
```
to do:

      - decide nak letak graph ke tak....
      - comment/ double check PR2.2-3.3
      - as of 13/4 [MAIN DUMP JE THE EQUATIONS...... TAK TUKAR PUN ON ANYTHING ELSE LAGI....]
  # Plot Directed Network Graph
  library(igraph)
  g <- graph_from_adjacency_matrix(A, mode = "directed", weighted = TRUE)
  plot(g,
       edge.width = E(g)$weight,
       main = "Player Network",
       vertex.size = 10,
       vertex.label.cex = 0.5,
       vertex.color = "skyblue",
       vertex.frame.color = "skyblue",
       vertex.shape = "circle",
       edge.width = 2,
       edge.color = "lightgrey",
       edge.arrow.size = 2,
       edge.arrow.width = 1.5)
  
      
```{r PR1}
PR1 <- function(match_history, alpha = 0.85, epsilon = 1e-6, max_iter = 10000) {
# Extract unique Player IDs
  playerID <- match_history %>%
    select(Winner, Loser) %>%
    unlist() %>%
    unique() %>%
    as.data.frame() %>%
    setNames("PlayerID")
  n <- nrow(playerID)
  
# Create edge weights
  edge_weights <- match_history %>%
    group_by(Winner, Loser) %>%
    summarise(weight = n(), .groups = "drop") %>%
    arrange(desc(weight))
  
# Map unique PlayerID to Indices
  ID <- playerID$PlayerID
  id_map <- setNames(seq_along(ID), ID) 
  edge_weights$Winner <- id_map[as.character(edge_weights$Winner)]
  edge_weights$Loser <- id_map[as.character(edge_weights$Loser)]
  
# 1. Create an adjacency matrix, A
  A <- matrix(0, nrow = n, ncol = n)
  rownames(A) <- ID
  colnames(A) <- ID
# Fill in the adjacency matrix using edge_weights
  for (i in 1:nrow(edge_weights)) {
    winner <- edge_weights$Winner[i]
    loser <- edge_weights$Loser[i]
    weight <- edge_weights$weight[i]
    A[winner, loser] <- weight  # row(winner), column(loser)
  }
  
# 2. Transition probability matrix, T
  T <- A
  w <- colSums(A) # Column sums (total matches loss for each player)
  for (i in 1:n) {
    if (w[i] > 0) { 
      T[,i] <- T[,i] / w[i] # Normalize rows for probability
    }
  }
  
# 3. Apply Damping factor to T to produce new Transition Probability matrix, P
  ones <- matrix(1, n, n)
  P <- ((1 - alpha) / n) * ones + alpha * T
  
# Initial distribution, x0
  x0 <- rep(1 / n, n) 
  
# 4. PageRank Iteration [Power Method]
  x <- x0  # Start with initial distribution
  iter <- 0  # Track number of iterations
  
  while (iter < max_iter) {
    x_new <- P %*% x  
    delta <- max(abs(x_new - x))  # Check change in PR values
    if (delta < epsilon) {
      break
    }
    x <- x_new 
    iter <- iter + 1
  }
  
# Normalize & Scale PageRank scores (for easier interpretation)
  pagerank_scores <- (x / sum(x))
  scaled_pagerank <- pagerank_scores * 10000
  ranked_players <- rank(-pagerank_scores, ties.method = "min")  
  
# Return results
  result <- data.frame(
    Rank = ranked_players,
    PlayerID = ID,
    PageRank = pagerank_scores,
    ScaledScore = scaled_pagerank,
    Iterations = iter
  ) %>%
    arrange(desc(PageRank))
  return(result)
}
```
```{r PR2.1}
PR2.1 <- function(match_history, alpha = 0.85, epsilon = 1e-6, max_iter = 10000, p = 1) {
# Same step as PR1
  playerID <- match_history %>%
    select(Winner, Loser) %>%
    unlist() %>%
    unique() %>%
    as.data.frame() %>%
    setNames("PlayerID")
  n <- nrow(playerID)
  
# Edge weights: Ratio of matches won
  edge_weights <- match_history %>%
    group_by(Winner, Loser) %>%
    summarise(weight = sum((Winner_Match_Won / (Winner_Match_Won +  Loser_Match_Won)), na.rm = TRUE), .groups = "drop") %>%
    arrange(desc(weight))
  
# Follows same steps as PR1
  ID <- playerID$PlayerID
  id_map <- setNames(seq_along(ID), ID) 
  edge_weights$Winner <- id_map[as.character(edge_weights$Winner)]
  edge_weights$Loser <- id_map[as.character(edge_weights$Loser)]
  A <- matrix(0, nrow = n, ncol = n)
  rownames(A) <- ID
  colnames(A) <- ID
  for (i in 1:nrow(edge_weights)) {
    winner <- edge_weights$Winner[i]
    loser <- edge_weights$Loser[i]
    weight <- edge_weights$weight[i]
    A[winner, loser] <- weight  
  }
  T <- A
  w <- colSums(A) 
  for (i in 1:n) {
    if (w[i] > 0) { 
      T[,i] <- T[,i] / w[i] 
    }
  }
  ones <- matrix(1, n, n)
  P <- ((1 - alpha) / n) * ones + alpha * T
  x0 <- rep(1 / n, n)  
  x <- x0  
  iter <- 0  
  while (iter < max_iter) {
    x_new <- P %*% x  
    delta <- max(abs(x_new - x)) 
    if (delta < epsilon) {
      break
    }
    x <- x_new  
    iter <- iter + 1
  }
  pagerank_scores <- (x / sum(x))
  scaled_pagerank <- pagerank_scores * 10000
  ranked_players <- rank(-pagerank_scores, ties.method = "min") 
  result <- data.frame(
    Rank = ranked_players,
    PlayerID = ID,
    PageRank = pagerank_scores,
    ScaledScore = scaled_pagerank,
    Iterations = iter
  ) %>%
    arrange(desc(PageRank)) 
  return(result)
}
```
```{r PR2.2}
PR2.2 <- function(match_history, alpha = 0.85, epsilon = 1e-6, max_iter = 10000, p = 1) {
# Same step as PR1
  playerID <- match_history %>%
    select(Winner, Loser) %>%
    unlist() %>%
    unique() %>%
    as.data.frame() %>%
    setNames("PlayerID")
  n <- nrow(playerID)
  
# Edge weights: Exponentiate ratio of matches won
  edge_weights <- match_history %>%
    group_by(Winner, Loser) %>%
    summarise(weight = sum((Winner_Match_Won / (Winner_Match_Won + Loser_Match_Won))^p, na.rm = TRUE), .groups = "drop") %>%
    arrange(desc(weight))
  
# Follows same steps as PR1
  ID <- playerID$PlayerID
  id_map <- setNames(seq_along(ID), ID) 
  edge_weights$Winner <- id_map[as.character(edge_weights$Winner)]
  edge_weights$Loser <- id_map[as.character(edge_weights$Loser)]
  A <- matrix(0, nrow = n, ncol = n)
  rownames(A) <- ID
  colnames(A) <- ID
  for (i in 1:nrow(edge_weights)) {
    winner <- edge_weights$Winner[i]
    loser <- edge_weights$Loser[i]
    weight <- edge_weights$weight[i]
    A[winner, loser] <- weight  
  }
  T <- A
  w <- colSums(A) 
  for (i in 1:n) {
    if (w[i] > 0) { 
      T[,i] <- T[,i] / w[i] 
    }
  }
  ones <- matrix(1, n, n)
  P <- ((1 - alpha) / n) * ones + alpha * T
  x0 <- rep(1 / n, n)  
  x <- x0  
  iter <- 0  
  while (iter < max_iter) {
    x_new <- P %*% x  
    delta <- max(abs(x_new - x)) 
    if (delta < epsilon) {
      break
    }
    x <- x_new  
    iter <- iter + 1
  }
  pagerank_scores <- (x / sum(x))
  scaled_pagerank <- pagerank_scores * 10000
  ranked_players <- rank(-pagerank_scores, ties.method = "min") 
  result <- data.frame(
    Rank = ranked_players,
    PlayerID = ID,
    PageRank = pagerank_scores,
    ScaledScore = scaled_pagerank,
    Iterations = iter
  ) %>%
    arrange(desc(PageRank)) 
  return(result)
}
```
```{r PR2.3}
PR2.3 <- function(match_history, alpha = 0.85, epsilon = 1e-6, max_iter = 10000, p = 1) {
# Same step as PR1
  playerID <- match_history %>%
    select(Winner, Loser) %>%
    unlist() %>%
    unique() %>%
    as.data.frame() %>%
    setNames("PlayerID")
  n <- nrow(playerID)
  
# Create Outcome from Winner_Match_Won & Loser_Match_Won
  match_history <- match_history %>%
    mutate(
      Outcome = paste(Winner_Match_Won, Loser_Match_Won, sep = "-")
    )

# Assign progressive weights based on Outcome
  edge_weights <- match_history %>%
    mutate(
      weight = case_when(
        Outcome == "2-0" ~ 1,
        Outcome == "2-1" ~ 1/2,
        Outcome == "3-0" ~ 1,
        Outcome == "3-1" ~ 2/3,
        Outcome == "3-2" ~ 1/3
      )
    ) %>%
    filter(!is.na(weight)) %>%
    group_by(Winner, Loser) %>%
    summarise(weight = sum(weight, na.rm = TRUE), .groups = "drop") %>%
    arrange(desc(weight))
  
# Follows same steps as PR1
  ID <- playerID$PlayerID
  id_map <- setNames(seq_along(ID), ID) 
  edge_weights$Winner <- id_map[as.character(edge_weights$Winner)]
  edge_weights$Loser <- id_map[as.character(edge_weights$Loser)]
  A <- matrix(0, nrow = n, ncol = n)
  rownames(A) <- ID
  colnames(A) <- ID
  for (i in 1:nrow(edge_weights)) {
    winner <- edge_weights$Winner[i]
    loser <- edge_weights$Loser[i]
    weight <- edge_weights$weight[i]
    A[winner, loser] <- weight  
  }
  T <- A
  w <- colSums(A) 
  for (i in 1:n) {
    if (w[i] > 0) { 
      T[,i] <- T[,i] / w[i] 
    }
  }
  ones <- matrix(1, n, n)
  P <- ((1 - alpha) / n) * ones + alpha * T
  x0 <- rep(1 / n, n)  
  x <- x0  
  iter <- 0  
  while (iter < max_iter) {
    x_new <- P %*% x  
    delta <- max(abs(x_new - x)) 
    if (delta < epsilon) {
      break
    }
    x <- x_new  
    iter <- iter + 1
  }
  pagerank_scores <- (x / sum(x))
  scaled_pagerank <- pagerank_scores * 10000
  ranked_players <- rank(-pagerank_scores, ties.method = "min") 
  result <- data.frame(
    Rank = ranked_players,
    PlayerID = ID,
    PageRank = pagerank_scores,
    ScaledScore = scaled_pagerank,
    Iterations = iter
  ) %>%
    arrange(desc(PageRank)) 
  return(result)
}
```
```{r PR3.1}
PR3.1 <- function(match_history, alpha = 0.85, epsilon = 1e-6, max_iter = 10000) {
  # Same step as PR1
  playerID <- match_history %>%
    select(Winner, Loser) %>%
    unlist() %>%
    unique() %>%
    as.data.frame() %>%
    setNames("PlayerID")
  n <- nrow(playerID)
  
    # Create edge weights based on TOTAL SCORE
  edge_weights <- match_history %>%
    group_by(Winner, Loser) %>%
    summarise(weight = sum(Win_points_total / (Win_points_total + Lose_points_total), na.rm = TRUE), .groups = "drop") %>%
    arrange(desc(weight))
  
# Follows same steps as PR1
  ID <- playerID$PlayerID
  id_map <- setNames(seq_along(ID), ID) 
  edge_weights$Winner <- id_map[as.character(edge_weights$Winner)]
  edge_weights$Loser <- id_map[as.character(edge_weights$Loser)]
  A <- matrix(0, nrow = n, ncol = n)
  rownames(A) <- ID
  colnames(A) <- ID
  for (i in 1:nrow(edge_weights)) {
    winner <- edge_weights$Winner[i]
    loser <- edge_weights$Loser[i]
    weight <- edge_weights$weight[i]
    A[winner, loser] <- weight  
  }
  T <- A
  w <- colSums(A) 
  for (i in 1:n) {
    if (w[i] > 0) { 
      T[,i] <- T[,i] / w[i] 
    }
  }
  ones <- matrix(1, n, n)
  P <- ((1 - alpha) / n) * ones + alpha * T
  x0 <- rep(1 / n, n)  
  x <- x0  
  iter <- 0  
  while (iter < max_iter) {
    x_new <- P %*% x  
    delta <- max(abs(x_new - x)) 
    if (delta < epsilon) {
      break
    }
    x <- x_new  
    iter <- iter + 1
  }
  pagerank_scores <- (x / sum(x))
  scaled_pagerank <- pagerank_scores * 10000
  ranked_players <- rank(-pagerank_scores, ties.method = "min") 
  result <- data.frame(
    Rank = ranked_players,
    PlayerID = ID,
    PageRank = pagerank_scores,
    ScaledScore = scaled_pagerank,
    Iterations = iter
  ) %>%
    arrange(desc(PageRank)) 
  return(result)
}
```
```{r PR3.2}
PR3.2 <- function(match_history, alpha = 0.85, epsilon = 1e-6, max_iter = 10000, p = 1) {
  # Same step as PR1
  playerID <- match_history %>%
    select(Winner, Loser) %>%
    unlist() %>%
    unique() %>%
    as.data.frame() %>%
    setNames("PlayerID")
  n <- nrow(playerID)
  
  # Define the adjustment function
  calculate_adjustment <- function(data, p) {
    data %>%
      rowwise() %>%
      mutate(
        # Adjustments for individual matches
        adjustment1 = ifelse(!is.na(Match1W) & !is.na(Match1L),
                           abs(Match1W - Match1L)^p, NA),
        adjustment2 = ifelse(!is.na(Match2W) & !is.na(Match2L),
                           abs(Match2W - Match2L)^p, NA),
        adjustment3 = ifelse(!is.na(Match3W) & !is.na(Match3L),
                           abs(Match3W - Match3L)^p, NA),
        adjustment4 = ifelse(!is.na(Match4W) & !is.na(Match4L),
                           abs(Match4W - Match4L)^p, NA),
        adjustment5 = ifelse(!is.na(Match5W) & !is.na(Match5L),
                           abs(Match5W - Match5L)^p, NA),
        # Average adjustment across all valid matches
        avg_adjustment = mean(c(adjustment1, adjustment2, adjustment3, adjustment4, adjustment5), na.rm = TRUE)
      ) %>%
      ungroup()
  }
  
  # Calculate edge weights with adjustment
  edge_weights_with_adjustment_H2H <- function(data, p) {
    data %>%
      calculate_adjustment(p = p) %>%
      filter(!is.na(avg_adjustment)) %>%
      group_by(Winner, Loser) %>%
      summarise(weight = sum(avg_adjustment, na.rm = TRUE), .groups = "drop")
  }
  
  edge_weights <- edge_weights_with_adjustment_H2H(match_history, p = p)
  
  # Follows same steps as PR1
  ID <- playerID$PlayerID
  id_map <- setNames(seq_along(ID), ID) 
  edge_weights$Winner <- id_map[as.character(edge_weights$Winner)]
  edge_weights$Loser <- id_map[as.character(edge_weights$Loser)]
  A <- matrix(0, nrow = n, ncol = n)
  rownames(A) <- ID
  colnames(A) <- ID
  for (i in 1:nrow(edge_weights)) {
    winner <- edge_weights$Winner[i]
    loser <- edge_weights$Loser[i]
    weight <- edge_weights$weight[i]
    A[winner, loser] <- weight  
  }
  T <- A
  w <- colSums(A) 
  for (i in 1:n) {
    if (w[i] > 0) { 
      T[,i] <- T[,i] / w[i] 
    }
  }
  ones <- matrix(1, n, n)
  P <- ((1 - alpha) / n) * ones + alpha * T
  x0 <- rep(1 / n, n)  
  x <- x0  
  iter <- 0  
  while (iter < max_iter) {
    x_new <- P %*% x  
    delta <- max(abs(x_new - x)) 
    if (delta < epsilon) {
      break
    }
    x <- x_new  
    iter <- iter + 1
  }
  pagerank_scores <- (x / sum(x))
  scaled_pagerank <- pagerank_scores * 10000
  ranked_players <- rank(-pagerank_scores, ties.method = "min") 
  result <- data.frame(
    Rank = ranked_players,
    PlayerID = ID,
    PageRank = pagerank_scores,
    ScaledScore = scaled_pagerank,
    Iterations = iter
  ) %>%
    arrange(desc(PageRank)) 
  return(result)
}
```
```{r PR3.3}
PR3.3 <- function(match_history, alpha = 0.85, epsilon = 1e-6, max_iter = 10000, p = 1) {
# Same step as PR1
  playerID <- match_history %>%
    select(Winner, Loser) %>%
    unlist() %>%
    unique() %>%
    as.data.frame() %>%
    setNames("PlayerID")
  n <- nrow(playerID)
  
# Adjustment Function
  calculate_adjustment <- function(data, p) {
    data %>%
      rowwise() %>%
      mutate(
        # Adjustments for individual matches
        adjustment1 = ifelse(!is.na(Match1W) & !is.na(Match1L),
                           abs(Match1W - Match1L)^p, NA),
        adjustment2 = ifelse(!is.na(Match2W) & !is.na(Match2L),
                           abs(Match2W - Match2L)^p, NA),
        adjustment3 = ifelse(!is.na(Match3W) & !is.na(Match3L),
                           abs(Match3W - Match3L)^p, NA),
        adjustment4 = ifelse(!is.na(Match4W) & !is.na(Match4L),
                           abs(Match4W - Match4L)^p, NA),
        adjustment5 = ifelse(!is.na(Match5W) & !is.na(Match5L),
                           abs(Match5W - Match5L)^p, NA),
        # Average adjustment across all valid matches
        avg_adjustment = mean(c(adjustment1, adjustment2, adjustment3, adjustment4, adjustment5), na.rm = TRUE)
      ) %>%
      ungroup()
  }
  
  # Edge Weights (adjustment * match_ratio)
  edge_weights_with_adjustment_H2H <- function(data, p) {
    data %>%
      calculate_adjustment(p = p) %>%
      mutate(
        # Adjust weight by the average adjustment and match ratio
        adjusted_weight = avg_adjustment * (Winner_Match_Won / (Winner_Match_Won + Loser_Match_Won))
      ) %>%
      group_by(Winner, Loser) %>%
      summarise(weight = sum(adjusted_weight, na.rm = TRUE), .groups = "drop")
  }
  
  edge_weights <- edge_weights_with_adjustment_H2H(match_history, p = p)
  
# Follows same steps as PR1
  ID <- playerID$PlayerID
  id_map <- setNames(seq_along(ID), ID) 
  edge_weights$Winner <- id_map[as.character(edge_weights$Winner)]
  edge_weights$Loser <- id_map[as.character(edge_weights$Loser)]
  A <- matrix(0, nrow = n, ncol = n)
  rownames(A) <- ID
  colnames(A) <- ID
  for (i in 1:nrow(edge_weights)) {
    winner <- edge_weights$Winner[i]
    loser <- edge_weights$Loser[i]
    weight <- edge_weights$weight[i]
    A[winner, loser] <- weight  
  }
  T <- A
  w <- colSums(A) 
  for (i in 1:n) {
    if (w[i] > 0) { 
      T[,i] <- T[,i] / w[i] 
    }
  }
  ones <- matrix(1, n, n)
  P <- ((1 - alpha) / n) * ones + alpha * T
  x0 <- rep(1 / n, n)  
  x <- x0  
  iter <- 0  
  while (iter < max_iter) {
    x_new <- P %*% x  
    delta <- max(abs(x_new - x)) 
    if (delta < epsilon) {
      break
    }
    x <- x_new  
    iter <- iter + 1
  }
  pagerank_scores <- (x / sum(x))
  scaled_pagerank <- pagerank_scores * 10000
  ranked_players <- rank(-pagerank_scores, ties.method = "min") 
  result <- data.frame(
    Rank = ranked_players,
    PlayerID = ID,
    PageRank = pagerank_scores,
    ScaledScore = scaled_pagerank,
    Iterations = iter
  ) %>%
    arrange(desc(PageRank)) 
  return(result)
}
```
```{r PR4}
PR4 <- function(match_history, alpha = 0.85, epsilon = 1e-6, max_iter = 10000) {
  # Same step as PR1
  playerID <- match_history %>%
    select(Winner, Loser) %>%
    unlist() %>%
    unique() %>%
    as.data.frame() %>%
    setNames("PlayerID")
  n <- nrow(playerID)
  
    # Create edge weights based on TOTAL SCORE
  edge_weights <- match_history %>%
    group_by(Winner, Loser) %>%
    summarise(weight = sum(Winner_Match_Won / (Winner_Match_Won + Loser_Match_Won)*level_weight*round_weight, na.rm = TRUE), .groups = "drop") %>%
    arrange(desc(weight))
  
  # Follows same steps as PR1
  ID <- playerID$PlayerID
  id_map <- setNames(seq_along(ID), ID) 
  edge_weights$Winner <- id_map[as.character(edge_weights$Winner)]
  edge_weights$Loser <- id_map[as.character(edge_weights$Loser)]
  A <- matrix(0, nrow = n, ncol = n)
  rownames(A) <- ID
  colnames(A) <- ID
  for (i in 1:nrow(edge_weights)) {
    winner <- edge_weights$Winner[i]
    loser <- edge_weights$Loser[i]
    weight <- edge_weights$weight[i]
    A[winner, loser] <- weight  
  }
  T <- A
  w <- colSums(A) 
  for (i in 1:n) {
    if (w[i] > 0) { 
      T[,i] <- T[,i] / w[i] 
    }
  }
  ones <- matrix(1, n, n)
  P <- ((1 - alpha) / n) * ones + alpha * T
  x0 <- rep(1 / n, n)  
  x <- x0  
  iter <- 0  
  while (iter < max_iter) {
    x_new <- P %*% x  
    delta <- max(abs(x_new - x)) 
    if (delta < epsilon) {
      break
    }
    x <- x_new  
    iter <- iter + 1
  }
  pagerank_scores <- (x / sum(x))
  scaled_pagerank <- pagerank_scores * 10000
  ranked_players <- rank(-pagerank_scores, ties.method = "min") 
  result <- data.frame(
    Rank = ranked_players,
    PlayerID = ID,
    PageRank = pagerank_scores,
    ScaledScore = scaled_pagerank,
    Iterations = iter
  ) %>%
    arrange(desc(PageRank)) 
  return(result)
}
```
```{r PR5}
PR5 <- function(match_history, latest_tournament, alpha = 0.85, epsilon = 1e-6, max_iter = 10000, p = 1, time_scale= 1) {
  # Same step as PR1
  playerID <- match_history %>%
    select(Winner, Loser) %>%
    unlist() %>%
    unique() %>%
    as.data.frame() %>%
    setNames("PlayerID")
  n <- nrow(playerID)
  
  # Adjustment Function (Same as PR3.3)
  calculate_adjustment <- function(data, p) {
    data %>%
      rowwise() %>%
      mutate(
        adjustment1 = ifelse(!is.na(Match1W) & !is.na(Match1L),
                           abs(Match1W - Match1L)^p, NA),
        adjustment2 = ifelse(!is.na(Match2W) & !is.na(Match2L),
                           abs(Match2W - Match2L)^p, NA),
        adjustment3 = ifelse(!is.na(Match3W) & !is.na(Match3L),
                           abs(Match3W - Match3L)^p, NA),
        adjustment4 = ifelse(!is.na(Match4W) & !is.na(Match4L),
                           abs(Match4W - Match4L)^p, NA),
        adjustment5 = ifelse(!is.na(Match5W) & !is.na(Match5L),
                           abs(Match5W - Match5L)^p, NA),
        avg_adjustment = mean(c(adjustment1, adjustment2, adjustment3, adjustment4, adjustment5), na.rm = TRUE)
      ) %>%
      ungroup()
  }
  match_history <- match_history %>%
    mutate(
      Outcome = paste(Winner_Match_Won, Loser_Match_Won, sep = "-")
    )
  # Match Scaling same as PR2.3
  match_history <- match_history %>%
    mutate(
      match_weight = case_when(
        Outcome == "2-0" ~ 1,
        Outcome == "2-1" ~ 1/2,
        Outcome == "3-0" ~ 1,
        Outcome == "3-1" ~ 2/3,
        Outcome == "3-2" ~ 1/3
      )
    )

  # Edge Weights: Adjusment Function (PR3.3) * Match Scaling (PR2.3) * Tournament and Round (PR4) * Time Scale
  edge_weights_with_adjustment_H2H <- function(data, p) {
    data %>%
      mutate(
        time_scale = if_else(
        Tournament_ID %in% latest_tournament, # If tournament ID is in the list of latest tournaments
        time_scale,1) # no boost otherwise
      )%>%
      # Include all components in adjusted edge weight
      calculate_adjustment(p = p) %>%
      mutate(
        adjusted_weight = avg_adjustment * match_weight * level_weight * round_weight * time_scale
      ) %>%
      group_by(Winner, Loser) %>%
      summarise(weight = sum(adjusted_weight, na.rm = TRUE), .groups = "drop")
  }
  
  edge_weights <- edge_weights_with_adjustment_H2H(match_history, p = p)
  
  
  # Follows same steps as PR1
  ID <- playerID$PlayerID
  id_map <- setNames(seq_along(ID), ID) 
  edge_weights$Winner <- id_map[as.character(edge_weights$Winner)]
  edge_weights$Loser <- id_map[as.character(edge_weights$Loser)]
  A <- matrix(0, nrow = n, ncol = n)
  rownames(A) <- ID
  colnames(A) <- ID
  for (i in 1:nrow(edge_weights)) {
    winner <- edge_weights$Winner[i]
    loser <- edge_weights$Loser[i]
    weight <- edge_weights$weight[i]
    A[winner, loser] <- weight  
  }
  T <- A
  w <- colSums(A) 
  for (i in 1:n) {
    if (w[i] > 0) { 
      T[,i] <- T[,i] / w[i] 
    }
  }
  ones <- matrix(1, n, n)
  P <- ((1 - alpha) / n) * ones + alpha * T
  x0 <- rep(1 / n, n)  
  x <- x0  
  iter <- 0  
  while (iter < max_iter) {
    x_new <- P %*% x  
    delta <- max(abs(x_new - x)) 
    if (delta < epsilon) {
      break
    }
    x <- x_new  
    iter <- iter + 1
  }
  pagerank_scores <- (x / sum(x))
  scaled_pagerank <- pagerank_scores * 10000
  ranked_players <- rank(-pagerank_scores, ties.method = "min") 
  result <- data.frame(
    Rank = ranked_players,
    PlayerID = ID,
    PageRank = pagerank_scores,
    ScaledScore = scaled_pagerank,
    Iterations = iter
  ) %>%
    arrange(desc(PageRank)) 
  return(result)
}
```

This next chunk is used to run the FULL cleaned dataset (without train-test split) on the final chosen optimised parameters of p and time_boost.

```{r Full run}
# PR1
PR1_MS <- PR1(MS)
PR1_WS <- PR1(WS)
PR1_MD <- PR1(MD)
PR1_WD <- PR1(WD)
PR1_XD <- PR1(XD)
# write.csv(PR1_MS, "PR1_MS.csv", row.names = FALSE, na="")
# write.csv(PR1_WS, "PR1_WS.csv", row.names = FALSE, na="")
# write.csv(PR1_MD, "PR1_MD.csv", row.names = FALSE, na="")
# write.csv(PR1_WD, "PR1_WD.csv", row.names = FALSE, na="")
# write.csv(PR1_XD, "PR1_XD.csv", row.names = FALSE, na="")

# PR2.1
PR2.1_MS <- PR2.1(MS)
PR2.1_WS <- PR2.1(WS)
PR2.1_MD <- PR2.1(MD)
PR2.1_WD <- PR2.1(WD)
PR2.1_XD <- PR2.1(XD)
# write.csv(PR2.1_MS, "PR2.1_MS.csv", row.names = FALSE, na="")
# write.csv(PR2.1_WS, "PR2.1_WS.csv", row.names = FALSE, na="")
# write.csv(PR2.1_MD, "PR2.1_MD.csv", row.names = FALSE, na="")
# write.csv(PR2.1_WD, "PR2.1_WD.csv", row.names = FALSE, na="")
# write.csv(PR2.1_XD, "PR2.1_XD.csv", row.names = FALSE, na="")

# PR2.2
PR2.2_MS <- PR2.2(MS, p= 0.5)
PR2.2_WS <- PR2.2(WS, p= 0.5)
PR2.2_MD <- PR2.2(MD, p= 0.5)
PR2.2_WD <- PR2.2(WD, p= 0.05)
PR2.2_XD <- PR2.2(XD, p= 0.5)
# write.csv(PR2.2_MS, "PR2.2_MS.csv", row.names = FALSE, na="")
# write.csv(PR2.2_WS, "PR2.2_WS.csv", row.names = FALSE, na="")
# write.csv(PR2.2_MD, "PR2.2_MD.csv", row.names = FALSE, na="")
# write.csv(PR2.2_WD, "PR2.2_WD.csv", row.names = FALSE, na="")
# write.csv(PR2.2_XD, "PR2.2_XD.csv", row.names = FALSE, na="")

# PR2.3
PR2.3_MS <- PR2.3(MS)
PR2.3_WS <- PR2.3(WS)
PR2.3_MD <- PR2.3(MD)
PR2.3_WD <- PR2.3(WD)
PR2.3_XD <- PR2.3(XD)
# write.csv(PR2.3_MS, "PR2.3_MS.csv", row.names = FALSE, na="")
# write.csv(PR2.3_WS, "PR2.3_WS.csv", row.names = FALSE, na="")
# write.csv(PR2.3_MD, "PR2.3_MD.csv", row.names = FALSE, na="")
# write.csv(PR2.3_WD, "PR2.3_WD.csv", row.names = FALSE, na="")
# write.csv(PR2.3_XD, "PR2.3_XD.csv", row.names = FALSE, na="")

# PR3.1
PR3.1_MS <- PR3.1(MS)
PR3.1_WS <- PR3.1(WS)
PR3.1_MD <- PR3.1(MD)
PR3.1_WD <- PR3.1(WD)
PR3.1_XD <- PR3.1(XD)
# write.csv(PR3.1_MS, "PR3.1_MS.csv", row.names = FALSE, na="")
# write.csv(PR3.1_WS, "PR3.1_WS.csv", row.names = FALSE, na="")
# write.csv(PR3.1_MD, "PR3.1_MD.csv", row.names = FALSE, na="")
# write.csv(PR3.1_WD, "PR3.1_WD.csv", row.names = FALSE, na="")
# write.csv(PR3.1_XD, "PR3.1_XD.csv", row.names = FALSE, na="")

# PR3.2
PR3.2_MS <- PR3.2(MS, p= 0.5)
PR3.2_WS <- PR3.2(WS, p= 0.5)
PR3.2_MD <- PR3.2(MD, p= 0.5)
PR3.2_WD <- PR3.2(WD, p= 3)
PR3.2_XD <- PR3.2(XD, p= 0.5)
# write.csv(PR3.2_MS, "PR3.2_MS.csv", row.names = FALSE, na="")
# write.csv(PR3.2_WS, "PR3.2_WS.csv", row.names = FALSE, na="")
# write.csv(PR3.2_MD, "PR3.2_MD.csv", row.names = FALSE, na="")
# write.csv(PR3.2_WD, "PR3.2_WD.csv", row.names = FALSE, na="")
# write.csv(PR3.2_XD, "PR3.2_XD.csv", row.names = FALSE, na="")

# PR3.3
PR3.3_MS <- PR3.3(MS, p= 0.5)
PR3.3_WS <- PR3.3(WS, p= 0.5)
PR3.3_MD <- PR3.3(MD, p= 0.5)
PR3.3_WD <- PR3.3(WD, p= 3)
PR3.3_XD <- PR3.3(XD, p= 0.5)
# write.csv(PR3.3_MS, "PR3.3_MS.csv", row.names = FALSE, na="")
# write.csv(PR3.3_WS, "PR3.3_WS.csv", row.names = FALSE, na="")
# write.csv(PR3.3_MD, "PR3.3_MD.csv", row.names = FALSE, na="")
# write.csv(PR3.3_WD, "PR3.3_WD.csv", row.names = FALSE, na="")
# write.csv(PR3.3_XD, "PR3.3_XD.csv", row.names = FALSE, na="")

# PR4
PR4_MS <- PR4(MS)
PR4_WS <- PR4(WS)
PR4_MD <- PR4(MD)
PR4_WD <- PR4(WD)
PR4_XD <- PR4(XD)
# write.csv(PR4_MS, "PR4_MS.csv", row.names = FALSE, na="")
# write.csv(PR4_WS, "PR4_WS.csv", row.names = FALSE, na="")
# write.csv(PR4_MD, "PR4_MD.csv", row.names = FALSE, na="")
# write.csv(PR4_WD, "PR4_WD.csv", row.names = FALSE, na="")
# write.csv(PR4_XD, "PR4_XD.csv", row.names = FALSE, na="")

# PR5
PR5_MS<-PR5(MS,latesttourID, p = 0.5, time_scale= 4.5)
PR5_WS<-PR5(WS,latesttourID, p = 0.5, time_scale= 5)
PR5_MD<-PR5(MD,latesttourID, p = 0.5, time_scale= 5)
PR5_WD<-PR5(WD,latesttourID, p = 3, time_scale= 5)
PR5_XD<-PR5(XD,latesttourID, p = 0.5, time_scale= 5)
# write.csv(PR5_MS, "PR5_MS.csv", row.names = FALSE, na="")
# write.csv(PR5_WS, "PR5_WS.csv", row.names = FALSE, na="")
# write.csv(PR5_MD, "PR5_MD.csv", row.names = FALSE, na="")
# write.csv(PR5_WD, "PR5_WD.csv", row.names = FALSE, na="")
# write.csv(PR5_XD, "PR5_XD.csv", row.names = FALSE, na="")
```

Run PR on dataset specific for Application (Tournament Decider & Betting Table)
```{r Application}
APP_MS<- read.csv("APPLICATION_MS.csv")
APP_WS<- read.csv("APPLICATION_WS.csv")
PR5_MS_APP<-PR5(APP_MS,latesttourID, p = 0.5, time_scale= 4.5)
PR5_WS_APP<-PR5(APP_WS,latesttourID, p = 0.5, time_scale= 5)
# write.csv(PR5_MS_APP, "APP_PR5_MS.csv", row.names = FALSE, na="")
# write.csv(PR5_WS_APP, "APP_PR5_WS.csv", row.names = FALSE, na="")
```
```{r Iteration}
P15 <- PR1(XD, alpha = 0.15)
P20 <- PR1(XD, alpha = 0.20)
P25 <- PR1(XD, alpha = 0.25)
P30 <- PR1(XD, alpha = 0.30)
P35 <- PR1(XD, alpha = 0.35)
P40 <- PR1(XD, alpha = 0.40)
P45 <- PR1(XD, alpha = 0.45)
P50 <- PR1(XD, alpha = 0.50)
P55 <- PR1(XD, alpha = 0.55)
P60 <- PR1(XD, alpha = 0.60)
P65 <- PR1(XD, alpha = 0.65)
P70 <- PR1(XD, alpha = 0.70)
P75 <- PR1(XD, alpha = 0.75)
P80 <- PR1(XD, alpha = 0.80)
P85 <- PR1(XD, alpha = 0.85)
P90 <- PR1(XD, alpha = 0.90)
P95 <- PR1(XD, alpha = 0.95)

P15$Iterations[1]
P20$Iterations[1]
P25$Iterations[1]
P30$Iterations[1]
P35$Iterations[1]
P40$Iterations[1]
P45$Iterations[1]
P50$Iterations[1]
P55$Iterations[1]
P60$Iterations[1]
P65$Iterations[1]
P70$Iterations[1]
P75$Iterations[1]
P80$Iterations[1]
P85$Iterations[1]
P90$Iterations[1]
P95$Iterations[1]
```